Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-20 tex/sections/consensus.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

For forking at block $h$, the reserve committee of delegates
makes a special \emph{fork block} which only contains a valid fork request, and its parent is the block $h$.
The height of the fork block therefore is $h + 1$, and the fork block needs a valid certificate from the assembly of
validators with the index $h+1$ modulo $m$. When a
fork block gets certified by validators, its parent is also confirmed and will become a part of the blockchain, even if
it does not have a validators certificate.

@@

For forking the blockchain, the reserve committee uses a straightforward algorithm. Let $h_v$ be the height of the last
block with a validator certificate and $h_v+k$ be the height of the last valid block that the reserve committee has
seen. For forking the main chain, the reserve committee generates all fork blocks with heights $h_v+1,h_v+2,\dots,
h_v+k+1$. The parent of the fork block with height $h_v+i$ will be the block $h_v+i-1$ of the main chain. Then the
reserve committee will wait until the fork block with height $h_v+k+1$ receives a certificate form validators. The
reserve committee then will continue the normal chain after that fork block and the fork block with height $h_v+k+1$
will be the parent of the first normal block generated by the reserve committee.

@@

If $h_{\max}$ denotes the height of the highest block with a validators certificate, as long as more than $2/3$ stake
of all the assemblies of validators are honest, for a fork block with height $h_f$ we have:
\begin{itemize}
    \item if $h_f \leq h_{\max}$, the fork block can not receive a certificate from validators.
    \item if $h_f = h_{\max} + 1$, the fork block may receive a certificate from validators or not. It is possible that
    the validators of the assembly with index $h_f$ modulo $m$ get divided between the fork block and a block at
    height $h_f$ of the main chain.
    \item if $h_f = h_{\max} + 2$, the fork block can always receive a certificate from validators, if network
    partitions do not last forever.
    \item if $h_f \geq h_{\max} + 3$, the fork block can always receive a certificate from validators \textbf{only if} a
    fork block at height $h_f-1$ gets certified by validators.
\end{itemize}

Consequently, if two fork blocks at heights $h_0$ and $h_0+k$ are generated by the reserve committee, if both blocks
receive a certified from validators, we must have $h_0 > h_{\max}$, and there must exist fork blocks with heights
$h_0+1,\dots,h_0+k-1$ which are certified by validators. That means if a malicious reserve committee generates a normal
block after any of the fork blocks with heights less than $h_0+k$, that normal block can not receive a certificate from
validators.

During the emergency forking, at max one block with a validators certificate may be discarded. This happens when
the malicious main committee of delegates has forked the main chain by producing blocks $b_1$ and $b_2$ at height
$h$; the block $b_1$ has received a validators certificate and validators have not certified any blocks at height $h+1$.
The reserve committee adds a fork block after block $b_2$ and that will discard $b_1$. Notice that if a block at
height $h+1$ had been certified by validators the fork block chould not have received a certificate from validators.

>>>>

For forking at block $h$, the reserve committee of delegates
makes a special \emph{fork block} which only contains a valid fork request, and its parent is the block $h$.
The height of the fork block therefore is $h + 1$, and the fork block needs a valid certificate from the assembly of
validators with index $h+1$ modulo $m$. When a
fork block gets certified by validators, its parent is also confirmed and will become a part of the blockchain, even if
it does not have a validators certificate.

@@

For forking the blockchain, the reserve committee uses a straightforward algorithm: let $h_v$ be the height of the last
block with a validator certificate and $h_v+k$ be the height of the last valid block that the reserve committee has
seen. For forking the main chain, the reserve committee generates all fork blocks with heights $h_v+1,h_v+2,\dots,
h_v+k+1$. The parent of the fork block with height $h_v+i$ will be the block $h_v+i-1$ of the main chain. The
reserve committee will wait until the fork block with height $h_v+k+1$ receives a certificate from validators and
then will continue the normal chain after that fork block. Hence, the fork block with height $h_v+k+1$
will be the parent of the first normal block generated by the reserve committee.

@@

If $h_{\max}$ denotes the height of the highest block with a validators certificate, as long as more than $2/3$ stake
of every assembly of validators are honest, for a fork block with height $h_f$ we have:\footnote{This fork block
forks the blockchain at height $h_f-1$.}
\begin{itemize}
    \item if $h_f \leq h_{\max}$, the fork block can not receive a certificate from validators.
    \item if $h_f = h_{\max} + 1$, the fork block may receive a certificate from validators or not. It is possible that
    the validators of the assembly with index $h_f$ modulo $m$ get divided between the fork block and a block at
    height $h_f$ of the main chain.
    \item if $h_f = h_{\max} + 2$, the fork block can always receive a certificate from validators, if network
    partitions do not last forever.
    \item if $h_f \geq h_{\max} + 3$, the fork block can always receive a certificate from validators \textbf{only if} a
    fork block at height $h_f-1$ gets certified by validators.
\end{itemize}

Consequently, if two fork blocks at heights $h_0$ and $h_0+k$ are generated by the reserve committee, if both blocks
receive a certified from validators, we must have $h_0 > h_{\max}$, and there must exist fork blocks with heights
$h_0+1,\dots,h_0+k-1$ which are certified by validators. That means if a malicious reserve committee generates a normal
block after any fork block with height less than $h_0+k$, that normal block can not receive a certificate from
validators.

During the emergency forking, at max one block with a validators certificate may be discarded. This happens when
the malicious main committee of delegates has forked the main chain by producing blocks $b_1$ and $b_2$ at height
$h$; the block $b_1$ has received a validators certificate and validators have not certified any blocks at height $h+1$.
The reserve committee adds a fork block whose parent is block $b_2$ and that will essentially discard $b_1$. Notice
that if a block at height $h+1$ had been certified by validators the fork block could not have received a certificate
from validators.
